Manuscript figures

### 2024-04-17 02a_manuscript_plots.Rmd
check paths

baselines <- model_meta |> 
  filter(model_id %in% c('persistenceRW', 'climatology'))
source('get_data.R')

@@

## Summary stats
```{r}
# total forecasts
distinct_forecasts <- arrow::open_dataset("./scores_2023") |> 
  distinct(model_id, site_id, variable, reference_datetime) |> 
  collect()

@@

ggpubr::ggarrange(top10_temp, all_temp, nrow = 1, align = 'hv',
                  common.legend = T,
                  legend = 'top', labels = 'auto') |> 
  ggsave(filename = './Plots/Figure2.png', width = 25, height = 11, units = 'cm')

>>>>

baselines <- model_meta |> 
  filter(model_id %in% c('persistenceRW', 'climatology'))
source('R/get_data.R')

@@

## Summary stats
```{r}
# total forecasts
distinct_forecasts <- arrow::open_dataset("./scores") |> 
  distinct(model_id, site_id, variable, reference_datetime) |> 
  collect()

@@
